SMT-Boosted Security Types for Low-Level MPC

### 2024-10-14 esop25/appendix.tex
checkpoint

    \eqj{R_1}{\eqs}{\toeq{\elab{\be}{\cid}}}{\ty_0}
  \end{mathpar}
  are both valid, and by the induction hypothesis $\Gamma_0$ is sound for $\prog_0$.
  We can then proceed by a second induction on the derivation of $\ty_0$, where there
  are two subcases defined by the $\TirName{DepTy}$ and $\TirName{Encode}$ rules.
  In the former case the result is immediate since all variables occuring in
  $\toeq{\elab{\be}{\cid}}$ are elements of $\ty_0$ by definition. In the latter case,
  we have:
  \begin{mathpar}
    \eqs \models \toeq{\elab{\be}{\cid}} \eop \phi' \fminus \rx{w}{\cid}

@@

A key observation is that, to undermine integrity adversarial strategies
must be different from passive strategies, in particular at least one
adversarial input must be different than any used in a passive strategy
(an abberation). 
\begin{definition}
  Given $H,C$ and $\prog$ with $\iov(\prog) = S \cup V \cup O$,
  we say $x \in V \cup O$ has an \emph{aberration} iff
  $\exists \adversary, \store \in \botruns(\prog)$ such that
  $\store(x) \ne \bot$ and $\neg\exists \store' \in \runs(\prog)$
  with  $\store_{S_H} = \store'_{S_H}$ and
  $\store(x) = \lcod{\store',\be}{\cid}$ where
  $\xassign{x}{\be}{\cid} \in \prog$.
\end{definition}
It is straightforward to prove that if an abberation can
exist, then it will be assigned $\lolab$ integrity in our
analysis. 
\begin{lemma}
  \label{lemma-aberration-low}
  Given protocol $\prog$ with
  $\views(\prog) = V$, if 
  $\ipj{\eqs}{\prog}{\Delta}$ is valid
  for some $\eqs$ and $x \in \cinputs$ has an
  aberration for some $H,C$, then $\cheatj{\Delta}{H,C}{\seclev}$
  and $\seclev(x) = \lolab$.
\end{lemma}
\begin{proof}
  Given $H,C$, \emph{every} adversarial input is assigned $\lolab$
  integrity by definition of the $\TirName{Mesg}$ rule and the
  \emph{leak} judgement.  The exception to this is messages that pass
  the $\TirName{MAC}$ check-- success of this check guarantees that
  the message is \emph{not} an aberration, so it can safely be
  switched to $\hilab$ integrity. \qed
\end{proof}
The following Lemma follows trivially by Definition \ref{def-integrity},
since without an aberration adversarial inputs are the same as some passive
strategy.
\begin{lemma}
  \label{lemma-undermined-logic}
  If $\prog$ with $\iov(\prog) = S \cup V \cup O$ does not have
  integrity for some $H,C$, then there exists $\setit{x} \cup V'
  \subseteq \cinputs$ where $\setit{x}$ has an aberration and
  $\notcondsep{\progd(\prog)}{S_H}{\setit{x} \cup V'}{\houtputs \cup O_H}$.
\end{lemma}

@@

Soundness of the $\metaprot$ type analysis follows mostly by a
straightforward mapping to the confidentiality and integrity type
systems. The most interesting rules are signature verification
($\TirName{Sig}$) and function application ($\TirName{App}$). 
Here the result hinges on the selection of ``fresh'' variables
that guarantee generalization of constraint entailment.
First we obtain a key result about instantiation and
satisfiability of constraints. 
\begin{lemma}
  \label{lemma-fresh}
  Given $w$ and $\cid$ with $\fresh(w,\cid)$, if $\notg{\eqs}[w/y_1,\cid/y_n]$
  is not satisfiable, then there exists no $w',\cid'$ such that
  $\notg{\eqs}[w'/y_1,\cid'/y_n]$ is satisifiable.
\end{lemma}

\begin{proof}
  Let $\eqs = \notg{\eqs}[w/y_1,\cid/y_n]$ and $\eqs' =
  \notg{\eqs}[w'/y_1,\cid'/y_n]$. If $w',\cid'$ are fresh or chosen
  such that $\eqs'$ is an $\alpha$-renaming of $\eqs$, the result is
  immediate.  Otherwise, it must be the case that at least two
  distinct variables $x_1$ and $x_2$ in $\eqs$ are renamed as a single
  variable $x$ in $\eqs'$, given freshness of $w,\cid$. Let
  $\mathit{rename}$ be the function that maps variables in $\eqs$ to
  variables in $\eqs'$ such that $\mathit{rename}(\eqs) = \eqs'$. Let
  $\store'$ be a model of $\eqs'$, and define $\store$ such that:
  $$
  \forall x \in \dom(\vars(E)) . \store(x) \defeq \store'(\mathit{rename}(x)) 
  $$
  Then $\store$ must be a model of $\eqs$, which is a contradiction. \qed
\end{proof}
Now we can extend the preceding Lemma to constraint entailment,
incorporating evaluation of expressions withing constraints. 
\begin{lemma}
  \label{lemma-eqs-notg}
  For all $\fresh(\mv_1,\ldots,\mv_n)$, $\notg{E_1}$, $\notg{E_2}$, assuming: 
  \begin{mathpar}
    \notg{\eqs_1}[\mv_1/y_1]\cdots[\mv_n/y_n]  \redx \eqs_1

>>>>

    \eqj{R_1}{\eqs}{\toeq{\elab{\be}{\cid}}}{\ty_0}
  \end{mathpar}
  are both valid, and by the induction hypothesis $\Gamma_0$ is sound for $\prog_0$.
  We can then proceed by a second induction on the derivation of $\ty_0$, where there
  are two subcases defined by the $\TirName{DepTy}$ and $\TirName{Encode}$ rules.
  In the former case the result is immediate since all variables occurring in
  $\toeq{\elab{\be}{\cid}}$ are elements of $\ty_0$ by definition. In the latter case,
  we have:
  \begin{mathpar}
    \eqs \models \toeq{\elab{\be}{\cid}} \eop \phi' \fminus \rx{w}{\cid}

@@

A key observation is that, to undermine integrity adversarial strategies
must be different from passive strategies, in particular at least one
adversarial input must be different than any used in a passive strategy
(an aberration). 
\begin{definition}
  Given $H,C$ and $\prog$ with $\iov(\prog) = S \cup V \cup O$,
  we say $x \in V \cup O$ has an \emph{aberration} iff
  $\exists \adversary, \store \in \botruns(\prog)$ such that
  $\store(x) \ne \bot$ and $\neg\exists \store' \in \runs(\prog)$
  with  $\store_{S_H} = \store'_{S_H}$ and
  $\store(x) = \lcod{\store',\be}{\cid}$ where
  $\xassign{x}{\be}{\cid} \in \prog$.
\end{definition}
It is straightforward to prove that if an aberration can
exist, then it will be assigned $\lolab$ integrity in our
analysis. 
\begin{lemma}
  \label{lemma-aberration-low}
  Given protocol $\prog$ with
  $\views(\prog) = V$, if 
  $\ipj{\eqs}{\prog}{\Delta}$ is valid
  for some $\eqs$ and $x \in \cinputs$ has an
  aberration for some $H,C$, then $\cheatj{\Delta}{H,C}{\seclev}$
  and $\seclev(x) = \lolab$.
\end{lemma}
\begin{proof}
  Given $H,C$, \emph{every} adversarial input is assigned $\lolab$
  integrity by definition of the $\TirName{Mesg}$ rule and the
  \emph{leak} judgement.  The exception to this is messages that pass
  the $\TirName{MAC}$ check-- success of this check guarantees that
  the message is \emph{not} an aberration, so it can safely be
  switched to $\hilab$ integrity. \qed
\end{proof}
The following Lemma follows trivially by Definition \ref{def-integrity},
since without an aberration adversarial inputs are the same as some passive
strategy.
\begin{lemma}
  \label{lemma-undermined-logic}
  If $\prog$ with $\iov(\prog) = S \cup V \cup O$ does not have
  integrity for some $H,C$, then there exists $\setit{x} \cup V'
  \subseteq \cinputs$ where $\setit{x}$ has an aberration and
  $\notcondsep{\progd(\prog)}{S_H}{\setit{x} \cup V'}{\houtputs \cup O_H}$.
\end{lemma}

@@

Soundness of the $\metaprot$ type analysis follows mostly by a
straightforward mapping to the confidentiality and integrity type
systems. The most interesting rules are signature verification
($\TirName{Sig}$) and function application ($\TirName{App}$). 
Here the result hinges on the selection of ``fresh'' variables
that guarantee generalization of constraint entailment.
First we obtain a key result about instantiation and
satisfiability of constraints. 
\begin{lemma}
  \label{lemma-fresh}
  Given $w$ and $\cid$ with $\fresh(w,\cid)$, if $\notg{\eqs}[w/y_1,\cid/y_n]$
  is not satisfiable, then there exists no $w',\cid'$ such that
  $\notg{\eqs}[w'/y_1,\cid'/y_n]$ is satisfiable.
\end{lemma}

\begin{proof}
  Let $\eqs = \notg{\eqs}[w/y_1,\cid/y_n]$ and $\eqs' =
  \notg{\eqs}[w'/y_1,\cid'/y_n]$. If $w',\cid'$ are fresh or chosen
  such that $\eqs'$ is an $\alpha$-renaming of $\eqs$, the result is
  immediate.  Otherwise, it must be the case that at least two
  distinct variables $x_1$ and $x_2$ in $\eqs$ are renamed as a single
  variable $x$ in $\eqs'$, given freshness of $w,\cid$. Let
  $\mathit{rename}$ be the function that maps variables in $\eqs$ to
  variables in $\eqs'$ such that $\mathit{rename}(\eqs) = \eqs'$. Let
  $\store'$ be a model of $\eqs'$, and define $\store$ such that:
  $$
  \forall x \in \dom(\vars(E)) . \store(x) \defeq \store'(\mathit{rename}(x)) 
  $$
  Then $\store$ must be a model of $\eqs$, which is a contradiction. \qed
\end{proof}
Now we can extend the preceding Lemma to constraint entailment,
incorporating evaluation of expressions within constraints. 
\begin{lemma}
  \label{lemma-eqs-notg}
  For all $\fresh(\mv_1,\ldots,\mv_n)$, $\notg{E_1}$, $\notg{E_2}$, assuming: 
  \begin{mathpar}
    \notg{\eqs_1}[\mv_1/y_1]\cdots[\mv_n/y_n]  \redx \eqs_1

### 2024-10-14 esop25/cpj.tex
checkpoint

The syntax of types $\ty$ and type environments $\Gamma$ are presented
in Figure \ref{fig-cpj}\footnote{In general we use $2^{\chi}$ to
denote the powerset of terms in any grammatical sort $\chi$.}. We also
define type judgements for expressions and programs by direct
interpretation as terms $\phi$ and constraints $\eqs$ respectively,
via the encoding $\toeq{\cdot}$. The \TirName{Encode} rule enforces
linearity by requiring that variables used for encryption are added to
judgements, and guaranteed to not be used elsewhere via a form of
union that ensures disjointness of combined sets:
\begin{definition}
  $R_1;R_2 = R_1 \cup R_2$ if $R_1 \cap R_2 = \varnothing$ and is otherwise
  undefined.
\end{definition}
The \TirName{DepTy} rule handles all cases and just records the
dependencies on variables in the term, a conservative approximation of
dependencies.  The \TirName{Send} rule records the types of messages,
reveals, and outputs in enviroments, and the \TirName{Seq} rule
combines the types of sequenced programs.  Given this we define
validity of program type judgements as follows.
\begin{definition}
  Given preprocessing predicate $\eqspre$ and protocol $\prog$ we say
  $\cpj{R}{\eqs}{\eqspre \wedge \toeq{\prog}}{\Gamma}$ is \emph{valid} iff it is derivable and
  $\eqspre \wedge \toeq{\prog} \models \eqs$.
\end{definition}
It is important to note that this presentation of derivations is
logical, not algorithmic-- in particular it is not syntax-directed
due to the \TirName{Encode} rule.

@@

Given a valid typing, we can leverage structural type information to
conservatively approximate the information accessible by the
adversary who has control over all corrupt clients in $C$ given
a partitioning $H,C$. In particular, if the adversary has access to an
encypted value and another value that is dependent on its one-time-pad
key-- i.e., access to values with types of the forms:
$$
\setit{\cty{\rx{w}{\cid}}{\ty}} \qquad \setit{\rx{w}{\cid}, \ldots} 
$$
then we can conservatively assume that the adversary can decrypt the
value of type $\ty$ and thus have access to those values.

@@

It is important to recall from \cite{skalka-near-ppdp24} that gradual
release does \emph{not} imply passive security, since it only concerns
adversarial messages, but not public reveals of outputs where
dependencies on input secrects can occur even in secure
protocols. Nevertheless, gradual release is an important
confidentiality property for MPC (and other distributed) protocols.

>>>>

The syntax of types $\ty$ and type environments $\Gamma$ are presented
in Figure \ref{fig-cpj}\footnote{In general we use $2^{\chi}$ to
denote the powerset of terms in any grammatical sort $\chi$.}. We also
define type judgements for expressions and programs by direct
interpretation as terms $\phi$ and constraints $\eqs$ respectively,
via the encoding $\toeq{\cdot}$. The \TirName{Encode} rule enforces
linearity by requiring that variables used for encryption are added to
judgements, and guaranteed to not be used elsewhere via a form of
union that ensures disjointness of combined sets:
\begin{definition}
  $R_1;R_2 = R_1 \cup R_2$ if $R_1 \cap R_2 = \varnothing$ and is otherwise
  undefined.
\end{definition}
The \TirName{DepTy} rule handles all cases and just records the
dependencies on variables in the term, a conservative approximation of
dependencies.  The \TirName{Send} rule records the types of messages,
reveals, and outputs in environments, and the \TirName{Seq} rule
combines the types of sequenced programs.  Given this we define
validity of program type judgements as follows.
\begin{definition}
  Given preprocessing predicate $\eqspre$ and protocol $\prog$ we say
  $\cpj{R}{\eqs}{\eqspre \wedge \toeq{\prog}}{\Gamma}$ is \emph{valid} iff it is derivable and
  $\eqspre \wedge \toeq{\prog} \models \eqs$.
\end{definition}
It is important to note that this presentation of derivations is
logical, not algorithmic-- in particular it is not syntax-directed
due to the \TirName{Encode} rule.

@@

Given a valid typing, we can leverage structural type information to
conservatively approximate the information accessible by the
adversary who has control over all corrupt clients in $C$ given
a partitioning $H,C$. In particular, if the adversary has access to an
encrypted value and another value that is dependent on its one-time-pad
key-- i.e., access to values with types of the forms:
$$
\setit{\cty{\rx{w}{\cid}}{\ty}} \qquad \setit{\rx{w}{\cid}, \ldots} 
$$
then we can conservatively assume that the adversary can decrypt the
value of type $\ty$ and thus have access to those values.

@@

It is important to recall from \cite{skalka-near-ppdp24} that gradual
release does \emph{not} imply passive security, since it only concerns
adversarial messages, but not public reveals of outputs where
dependencies on input secrets can occur even in secure
protocols. Nevertheless, gradual release is an important
confidentiality property for MPC (and other distributed) protocols.

### 2024-10-14 esop25/examples.tex
checkpoint

Using the Satisfiability Modulo Fields theory in cvc5 on an Apple M1
processor, we have verified correctness of additive sharing protocols
in fields up to size $\fieldp{2^{31} - 1}$ (an approximation of 32-bit
integers) which takes ~7ms to compute for 3 parties and not
significantly more than for, e.g., $\fieldp{2}$. We have also verified
the semi-homorphic encryption properties leveraged in the BDOZ circuit
library functions (Figures \ref{fig-bdozsum} and \ref{fig-bdozmult}) in
fields up to size $\fieldp{2^{31} - 1}$ which take ~8ms for the
property used for the postcondition of the $\ttt{mult}$ gate. This is
categorically better performance than can be achieved using previous
brute-force methods in $\fieldp{2}$ \cite{skalka-near-ppdp24}.

@@

A common approach to implementing multiplication gates in a BDOZ
setting is to use \emph{Beaver Triples}. Recall that Beaver triples
are values $a,b,c$ with $a$ and $b$ chosen randomly and $c = a * b$,
unique per multiplication gate, that are secret shared with clients
during pre-processing.  In our encoding we assume the additional
convention that each gate output identifier distinguishes the Beaver
triple, so for example the share of the $a$ value for a gate
$\ttt{"g1"}$ is identified by $\ttt{"g1as"}$, etc., and $\eqspre$
subsumes the following constraints for the $a,b,c$ values of gate
$\ttt{"g1"}$.  {\footnotesize$$
\begin{array}{l}
\mx{\ttt{"g1as"}}{1} \eop \rx{\ttt{"g1as"}}{1}\ \wedge 
\mx{\ttt{"g1bs"}}{1} \eop \rx{\ttt{"g1bs"}}{1}\ \wedge\\
\mx{\ttt{"g1as"}}{2} \eop \rx{\ttt{"g1as"}}{2}\ \wedge 
\mx{\ttt{"g1bs"}}{2} \eop \rx{\ttt{"g1bs"}}{2}\ \wedge\\
\mx{\ttt{"g1cs"}}{1} \eop \\
\qquad ((\mx{\ttt{"g1as"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})\ \ftimes\\
\qquad\phantom{(}(\mx{\ttt{"g1bs"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})) \fminus \rx{\ttt{"g1cs"}}{2}\ \wedge\\
\mx{\ttt{"g1cs"}}{2} \eop \rx{\ttt{"g1cs"}}{2}
\end{array}
$$}
The definition of the $\ttt{mult}$ gate is presented in Figure
\ref{fig-bdozmult}, where we present just client 1's side of the
protocol $\ttt{\_mult1}$ (client 2's side is nearly symmetric but with
a small variation-- refer to
\cite{evans2018pragmatic,10.1007/978-3-030-68869-1_3} for more
details).  We could call this function on input secrets
$\sx{\ttt{"x"}}{1}$ and $\sx{\ttt{"y"}}{2}$ in gate $\ttt{"g1"}$ as
$\ttt{mult}(\ttt{"g1"},\ttt{"x"},\ttt{"y"})$, for example, or embed
this gate internally in a circuit.

As for $\ttt{\_sum}$, the postcondition of the $\ttt{\_mult1}$
function expresses the relevant semi-homorphic encryption property of
the resulting share, MAC, and key after gate execution-- specifically,
it preserves the BDOZ authentication property. The precondition that
input shares must possess this property is enforced by the two calls
to $\ttt{sum}$ within the body of $\ttt{mult}$ and need not be made
explicit. Finally, the postcondition of $\ttt{mult}$ expresses the
correctness property of the multiplication gate. In any case,
integrity of any circuit constructed from the $\ttt{sum}$ and
$\ttt{mult}$ library functions will require little MPC.

>>>>

To evaluate our system especially regarding performance, using the
Satisfiability Modulo Fields theory in cvc5 on an Apple M1 processor,
we have verified correctness of additive sharing protocols in fields
up to size $\fieldp{2^{31} - 1}$ (an approximation of 32-bit integers)
which takes $\sim$7ms to compute for 3 parties and not significantly more
than for, e.g., $\fieldp{2}$. We have also verified the semi-homomorphic
encryption properties leveraged in the BDOZ circuit library functions
(Figures \ref{fig-bdozsum} and \ref{fig-bdozmult}) in fields up to
size $\fieldp{2^{31} - 1}$ which take $\sim$8ms for the property used for
the postcondition of the $\ttt{mult}$ gate. This is categorically
better performance than can be achieved using previous brute-force
methods in $\fieldp{2}$ \cite{skalka-near-ppdp24}.

@@

A common approach to implementing multiplication gates in a BDOZ
setting is to use \emph{Beaver Triples}. Recall that Beaver triples
are values $a,b,c$ with $a$ and $b$ chosen randomly and $c = a * b$,
unique per multiplication gate, that are secret shared with clients
during pre-processing.  In our encoding we assume the additional
convention that each gate output identifier distinguishes the Beaver
triple, so for example the share of the $a$ value for a gate
$\ttt{"g1"}$ is identified by $\ttt{"g1as"}$, etc., and $\eqspre$
subsumes the following constraints for the $a,b,c$ values of gate
$\ttt{"g1"}$.  {\footnotesize$$
\begin{array}{l}
\mx{\ttt{"g1as"}}{1} \eop \rx{\ttt{"g1as"}}{1}\ \wedge 
\mx{\ttt{"g1bs"}}{1} \eop \rx{\ttt{"g1bs"}}{1}\ \wedge\\
\mx{\ttt{"g1as"}}{2} \eop \rx{\ttt{"g1as"}}{2}\ \wedge 
\mx{\ttt{"g1bs"}}{2} \eop \rx{\ttt{"g1bs"}}{2}\ \wedge\\
\mx{\ttt{"g1cs"}}{1} \eop \\
\qquad ((\mx{\ttt{"g1as"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})\ \ftimes\\
\qquad\phantom{(}(\mx{\ttt{"g1bs"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})) \fminus \rx{\ttt{"g1cs"}}{2}\ \wedge\\
\mx{\ttt{"g1cs"}}{2} \eop \rx{\ttt{"g1cs"}}{2}
\end{array}
$$}

The definition of the $\ttt{mult}$ gate is presented in Figure
\ref{fig-bdozmult}, where we present just client 1's side of the
protocol $\ttt{\_mult1}$ (client 2's side is nearly symmetric but with
a small variation-- refer to
\cite{evans2018pragmatic,10.1007/978-3-030-68869-1_3} for more
details).  We could call this function on input secrets
$\sx{\ttt{"x"}}{1}$ and $\sx{\ttt{"y"}}{2}$ in gate $\ttt{"g1"}$ as
$\ttt{mult}(\ttt{"g1"},\ttt{"x"},\ttt{"y"})$, for example, or embed
this gate internally in a circuit.

As for $\ttt{\_sum}$, the postcondition of the $\ttt{\_mult1}$
function expresses the relevant semi-homomorphic encryption property of
the resulting share, MAC, and key after gate execution-- specifically,
it preserves the BDOZ authentication property. The precondition that
input shares must possess this property is enforced by the two calls
to $\ttt{sum}$ within the body of $\ttt{mult}$ and need not be made
explicit. Finally, the postcondition of $\ttt{mult}$ expresses the
correctness property of the multiplication gate. In any case,
integrity of any circuit constructed from the $\ttt{sum}$ and
$\ttt{mult}$ library functions will require little SMT overhead
due to compositional verification.

### 2024-10-14 esop25/intro.tex
checkpoint

The most closely related work is \cite{skalka-near-ppdp24}, where
foundations for $\minicat/\metaprot$ are introduced including a
verification algorithm. However, this algorithm only works for
$\mathbb{F}_2$-- e.g., binary circuits-- and does not scale due to
exponential complexity, necessitating semi-automated proof
techniqued. In contrast, our type systems scale to arbitrary prime
fields and whole program analysis for larger circuits (protocols). So
our work is a significant advancement of $\minicat/\metaprot$.  Out
work is also closely related to Satisfiability Modulo Finite Fields
\cite{SMFF} but only in the sense that we apply their method as we
discuss in Section \ref{section-smt} and subsequently.

>>>>

The most closely related work is \cite{skalka-near-ppdp24}, where
foundations for $\minicat/\metaprot$ are introduced including a
verification algorithm. However, this algorithm only works for
$\mathbb{F}_2$-- e.g., binary circuits-- and does not scale due to
exponential complexity, necessitating semi-automated proof
techniques. In contrast, our type systems scale to arbitrary prime
fields and whole program analysis for larger circuits (protocols). So
our work is a significant advancement of $\minicat/\metaprot$.  Out
work is also closely related to Satisfiability Modulo Finite Fields
\cite{SMFF} but only in the sense that we apply their method as we
discuss in Section \ref{section-smt} and subsequently.

### 2024-10-14 esop25/lang.tex
checkpoint

Our semantics require that random tapes contain values for all program
values $\elab{\flip{w}}{\cid}$ sampled from a uniform distribution
over $\mathbb{F}_p$. Input memories also contain input secret values
and possibly other initial view elements as a result of
pre-processing, e.g., Beaver triples for efficient multiplication,
and/or MACed share distributions as in BDOZ/SPDZ
\cite{evans2018pragmatic,10.1007/978-3-030-68869-1_3}. We define
$\runs(\prog)$ as the set of final memories resulting from execution
of $\prog$ given any initial memory, possibly augmented with a
preprocessed memory (a memory that satsfies a predicate $\preproc$),
and $\aruns(\prog)$ is the analog in the malicious setting. Since we
constrain programs to not overwrite any variable, we are assured that
final memories contain both a complete record of all initial secrets
as well as views resulting from communicated information. This
formulation will be fundamental to our consideration of probability
distributions and hyperproperties of protocols.
%In this
%setting, given a program $\prog$ with $\iov(\prog) = S \cup V$ and
%$\flips(\prog) = F$ we will consider all $\store \in \mems(S \cup V
%\cup F)$ such that $ \config{\store_{S \cup F}}{\prog} \redxs
%\config{\store_}{\varnothing} $ to be equally probable, establishing
%the basic distribution of the program. %From this, we can immediately
%derive the marginal distribution of $S \cup V$ to reason about
%dependencies between secrets and views.
\begin{definition}
  \label{def-runs}
  Given $\prog$ with $\secrets(\prog) = S$ and $\flips(\prog) = R$ and
  predicate $\preproc$ on memories, define:
  $$
  \begin{array}{c}
    \runs(\prog) \defeq 
    \{ \store \mid \exists \store_1 \in \mems(S \cup R) . 
    \exists \store_2 . \preproc(\store_2) \wedge
    %(\dom(\store) = \iov(\prog) \cup R) \wedge
    (\store_1 \uplus \store_2,\prog) \redxs \store \}
  \end{array}
  $$
  And similarly for any $\adversary$ define:
  $$
  \begin{array}{c}
    \aruns(\prog) \defeq 
    \{ \store \mid \exists \store_1 \in \mems(S \cup R) . 
    \exists \store_2 . \preproc(\store_2) \wedge
    %(\dom(\store) = \iov(\prog) \cup R) \wedge
    (\store_1 \uplus \store_2,\prog) \aredxs \store \}
  \end{array}
  $$
\end{definition}

>>>>

Our semantics require that random tapes contain values for all program
values $\elab{\flip{w}}{\cid}$ sampled from a uniform distribution
over $\mathbb{F}_p$. Input memories also contain input secret values
and possibly other initial view elements as a result of
pre-processing, e.g., Beaver triples for efficient multiplication,
and/or MACed share distributions as in BDOZ/SPDZ
\cite{evans2018pragmatic,10.1007/978-3-030-68869-1_3}. We define
$\runs(\prog)$ as the set of final memories resulting from execution
of $\prog$ given any initial memory, possibly augmented with a
preprocessed memory (a memory that satisfies a predicate $\preproc$),
and $\aruns(\prog)$ is the analog in the malicious setting. Since we
constrain programs to not overwrite any variable, we are assured that
final memories contain both a complete record of all initial secrets
as well as views resulting from communicated information. This
formulation will be fundamental to our consideration of probability
distributions and hyperproperties of protocols.
%In this
%setting, given a program $\prog$ with $\iov(\prog) = S \cup V$ and
%$\flips(\prog) = F$ we will consider all $\store \in \mems(S \cup V
%\cup F)$ such that $ \config{\store_{S \cup F}}{\prog} \redxs
%\config{\store_}{\varnothing} $ to be equally probable, establishing
%the basic distribution of the program. %From this, we can immediately
%derive the marginal distribution of $S \cup V$ to reason about
%dependencies between secrets and views.
\begin{definition}
  \label{def-runs}
  Given $\prog$ with $\secrets(\prog) = S$ and $\flips(\prog) = R$ and
  predicate $\preproc$ on memories, define:
  $$
  \begin{array}{c}
    \runs(\prog) \defeq 
    \{ \store \mid \exists \store_1 \in \mems(S \cup R) . 
    \exists \store_2 . \preproc(\store_2) \wedge
    %(\dom(\store) = \iov(\prog) \cup R) \wedge
    (\store_1 \uplus \store_2,\prog) \redxs \store \}
  \end{array}
  $$
  And similarly for any $\adversary$ define:
  $$
  \begin{array}{c}
    \aruns(\prog) \defeq 
    \{ \store \mid \exists \store_1 \in \mems(S \cup R) . 
    \exists \store_2 . \preproc(\store_2) \wedge
    %(\dom(\store) = \iov(\prog) \cup R) \wedge
    (\store_1 \uplus \store_2,\prog) \aredxs \store \}
  \end{array}
  $$
\end{definition}

### 2024-10-14 esop25/metalang.tex
checkpoint

We generalize these benefits of compositional verification by allowing
pre- and post-condition annotations on $\metaprot$ functions. For
example, consider a GMW-style, 2-party ``and-gate'' function
$\ttt{andgmw}(x,y,z)$. In this protocol, each party $\cid
\in \{1,2\}$ holds an additive secret share $\mx{x}{\cid}$ of
values identified by $x$ and $y$, and at the end of the
protocol each hold a secret share $\mx{z}{\cid}$, where:
$$
\mx{z}{1} \fplus \mx{z}{2} \eop (\mx{x}{1} \fplus \mx{x}{2}) \ftimes (\mx{y}{1} \fplus \mx{y}{2})
$$
We provide details of $\ttt{andgmw}$ and other GMW protocol
elements in Section \ref{section-examples}.  Our point now is that,
similarly to the $\ttt{encode}$ example, we can verify this
post-condition once as a correctness property for $\ttt{andgmw}$, and
then integrate instances of it into circuit correctness properties
with the guarantee that each instance also holds for any
$\ttt{andgmw}$ gate.  Since the program logic of $\ttt{andgmw}$ is
non-trivial, and typical circuits can use up to thousands of gates,
this has significant practical benefits by greatly reducing SMT overhead
in whole-program analysis.

@@

Hoare-style types for instructions have the following form:
$$
\hty{\eqs_1}{\Gamma}{R}{\Delta}{\eqs_2}
$$
Here, $\eqs_1$ and $\eqs_2$ are the pre- and postconditions
respectively, $\Gamma$ is the confidentiality type environment of the
protocol resulting from execution of the instruction, which is sound
wrt confidentiality typing, $R$ are the one-time-pads consumed in the
confidentialty typing, and $\Delta$ is the sound integrity type
environment.

@@

To obtain high precision in the type system, and to generalize
functions typings, we also introduce a form of type dependency,
specifically dependence on $\metaprot$ expressions. Dependent
$\Pi$ types have the form:
$$
\dht{y_1,\ldots,y_n}{\notg{\eqs_1}}{\notg{\Gamma}}{\notg{R}}{\notg{\Delta}}{\notg{\eqs_2}}
$$
where $y_1,\ldots,y_n$ range over values $\mv$ and each of
$\notg{\eqs_1}$ etc.~may contain expressions with free occurences
of $y_1,\ldots,y_n$-- the syntax of these forms is in Figure
\ref{fig-notg}. These $\Pi$ types are assigned to functions
and instantiated at application points.

>>>>

We generalize these benefits of compositional verification by allowing
pre-~and postcondition annotations on $\metaprot$ functions. For
example, consider a GMW-style, 2-party ``and-gate'' function
$\ttt{andgmw}(x,y,z)$. In this protocol, each party $\cid
\in \{1,2\}$ holds an additive secret share $\mx{x}{\cid}$ of
values identified by $x$ and $y$, and at the end of the
protocol each hold a secret share $\mx{z}{\cid}$, where:
$$
\mx{z}{1} \fplus \mx{z}{2} \eop (\mx{x}{1} \fplus \mx{x}{2}) \ftimes (\mx{y}{1} \fplus \mx{y}{2})
$$
We provide details of $\ttt{andgmw}$ and other GMW protocol
elements in Section \ref{section-examples}.  Our point now is that,
similarly to the $\ttt{encode}$ example, we can verify this
postcondition once as a correctness property for $\ttt{andgmw}$, and
then integrate instances of it into circuit correctness properties
with the guarantee that each instance also holds for any
$\ttt{andgmw}$ gate.  Since the program logic of $\ttt{andgmw}$ is
non-trivial, and typical circuits can use up to thousands of gates,
this has significant practical benefits by greatly reducing SMT overhead
in whole-program analysis.

@@

Hoare-style types for instructions have the following form:
$$
\hty{\eqs_1}{\Gamma}{R}{\Delta}{\eqs_2}
$$
Here, $\eqs_1$ and $\eqs_2$ are the pre- and postconditions
respectively, $\Gamma$ is the confidentiality type environment of the
protocol resulting from execution of the instruction, which is sound
wrt confidentiality typing, $R$ are the one-time-pads consumed in the
confidentiality typing, and $\Delta$ is the sound integrity type
environment.

@@

To obtain high precision in the type system, and to generalize
functions typings, we also introduce a form of type dependency,
specifically dependence on $\metaprot$ expressions. Dependent
$\Pi$ types have the form:
$$
\dht{y_1,\ldots,y_n}{\notg{\eqs_1}}{\notg{\Gamma}}{\notg{R}}{\notg{\Delta}}{\notg{\eqs_2}}
$$
where $y_1,\ldots,y_n$ range over values $\mv$ and each of
$\notg{\eqs_1}$ etc.~may contain expressions with free occurrences
of $y_1,\ldots,y_n$-- the syntax of these forms is in Figure
\ref{fig-notg}. These $\Pi$ types are assigned to functions
and instantiated at application points.

### 2024-10-14 esop25/model.tex
checkpoint

\emph{Integrity} is an important hyperproperty in security models that
admit malicious adversaries. Consistent with formulations in
deterministic settings, we define protocol integrity as the
preservation of high equivalence (of secrets and views). Intuitively,
this property says that any adversarial strategy either ``mimics'' a
passive strategy with some choice of inputs or causes an abort.
\begin{definition}[Integrity]
  \label{def-integrity}
  We say that a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ has
  \emph{integrity} iff for all $H$, $C$, and $\adversary$,
  if $\store \in \aruns(\prog)$ 
  then there exists $\store' \in \mems(S)$ with $\store_{S_H} = \store'_{S_H} $ and:
    $$
    \condd{\progtt(\prog,\adversary)}{X}{\store_{S_H \cup \cinputs}} =
    \condd{\progtt(\prog)}{X}{\store'}
    $$ 
  where $X \defeq (\houtputs \cup O_H) \cap \dom(\store)$. 
\end{definition}
Integrity plus noninteference modulo output implies malicious security
in the real/ideal model \cite{skalka-near-ppdp24}, and integrity plus
gradual release is a probabilistic form of robust declassification
\cite{sabelfeld2009declassification}.

>>>>

\emph{Integrity} is an important hyperproperty in security models that
admit malicious adversaries. Consistent with formulations in
deterministic settings, we define protocol integrity as the
preservation of high equivalence (of secrets and views). Intuitively,
this property says that any adversarial strategy either ``mimics'' a
passive strategy with some choice of inputs or causes an abort.
\begin{definition}[Integrity]
  \label{def-integrity}
  We say that a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ has
  \emph{integrity} iff for all $H$, $C$, and $\adversary$,
  if $\store \in \aruns(\prog)$ 
  then there exists $\store' \in \mems(S)$ with $\store_{S_H} = \store'_{S_H} $ and:
    $$
    \condd{\progtt(\prog,\adversary)}{X}{\store_{S_H \cup \cinputs}} =
    \condd{\progtt(\prog)}{X}{\store'}
    $$ 
  where $X \defeq (\houtputs \cup O_H) \cap \dom(\store)$. 
\end{definition}
Integrity plus noninterference modulo output implies malicious security
in the real/ideal model \cite{skalka-near-ppdp24}, and integrity plus
gradual release is a probabilistic form of robust declassification
\cite{sabelfeld2009declassification}.
